---
title: Qualitative Analysis of Focus Group Data
output: html_document
---

# Introduction
This RMarkdown document provides documentation for the code that performs qualitative analysis on the results of a focus group. The code demonstrates techniques such as coding, categorizing, and analyzing the data using the `tm`, `dplyr`, and `ggplot2` packages in R.

## Step 1: Load Required Libraries
```{r eval = FALSE}
library(tm)      # Text mining
library(dplyr)   # Data manipulation
library(ggplot2) # Data visualization
```

## Step 2: Define the Focus Group Data
Replace the focus_group variable with your own focus group data. The data should be stored as a character vector, where each element represents a participant's response.

```{r eval = FALSE}
focus_group <- c(
  "Participant 1: I really liked the new product. It's innovative and useful.",
  "Participant 2: The product design could be improved. It's not user-friendly.",
  "Participant 3: I found the product to be too expensive for what it offers.",
  "Participant 4: The customer support was excellent. They were very responsive.",
  "Participant 5: I didn't understand how to use the product. It needs better instructions."
)
```

## Step 3: Create a Document-Term Matrix
The code converts the focus group data into a document-term matrix using the tm package. The matrix represents the frequency of words in the focus group responses.

```{r eval = FALSE}
corpus <- Corpus(VectorSource(focus_group))
corpus <- tm_map(corpus, content_transformer(tolower))
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, removeNumbers)
corpus <- tm_map(corpus, removeWords, stopwords("english"))
corpus <- tm_map(corpus, stripWhitespace)
dtm <- DocumentTermMatrix(corpus)

```

## Step 4: Convert the Document-Term Matrix to a Data Frame
The document-term matrix is converted to a data frame for further analysis. Each row of the data frame represents a document (participant response), and each column represents a term (word).

```{r eval = FALSE}
dtm_df <- as.data.frame(as.matrix(dtm))
dtm_df <- dtm_df %>%
  mutate(Document = row.names(.)) %>%
  select(Document, everything())
```

## Step 5: Perform Coding and Categorization
The code assigns coding labels (e.g., "Positive" or "Negative") to each document based on their content. Modify the coding labels and conditions according to your analysis requirements.

```{r eval = FALSE}
dtm_df$coding <- NA
dtm_df$coding[dtm_df$Document == "Participant 1"] <- "Positive"
dtm_df$coding[dtm_df$Document == "Participant 2"] <- "Negative"
dtm_df$coding[dtm_df$Document == "Participant 3"] <- "Negative"
dtm_df$coding[dtm_df$Document == "Participant 4"] <- "Positive"
dtm_df$coding[dtm_df$Document == "Participant 5"] <- "Negative"
```

## Step 6: Analyze and Visualize the Coding Results
The code summarizes the coding results and creates a bar plot to visualize the counts of each coding category.

```{r eval = FALSE}
coding_summary <- dtm_df %>%
  group_by(coding) %>%
  summarize(count = n())
```

